Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

Comparing these results with those obtained from student surveys in
\cite{MoraChatbots2021:anon}, we now have a clear vision of the differences
between teachers' and students' points of view and intentions when using the
messaging applications in higher education. Teachers are more likely to adopt
technologies that are supported by their institutions. This may be driven by a
desire to ensure that their universities monitor and support their efforts
to assist students during the learning process, although another reason could
simply be their familiarity with the technological services provided by their
institutions. Meanwhile, students use non-institution messaging applications to
create informal discussion groups with their peers. It is worth noting that peer
support and collaboration are inseparable from learning
\cite{timmis2012constant} and its presence correlates positively with higher
retention in higher education \cite{o2014front}. Therefore, both perspectives
are complementary and play different roles in promoting the learning process;
however, there is a certain degree of incompatibility that would hinder the
process of adoption of a single messaging service that fits the need of both
collectives, or would favor the adoption of semi-informal solutions that would
rely on a popular platform (such as WhatsApp or Telegram) enhanced with
institutional agreements with their providers, as well as locally created and
supported chatbots.

>>>>

Comparing these results with those obtained from student surveys in
\cite{MoraChatbots2021:anon}, we now have a clear vision of the differences
between teachers' and students' points of view and intentions when using the
messaging applications in higher education. Teachers are more likely to adopt
technologies that are supported by their institutions. This may be driven by a
desire to ensure that their universities monitor and support their efforts
to assist students during the learning process, although another reason could
simply be their familiarity with the technological services provided by their
institutions. Meanwhile, students use non-institutional messaging applications to
create informal discussion groups with their peers. It is worth noting that peer
support and collaboration are inseparable from learning
\cite{timmis2012constant} and its presence correlates positively with higher
retention rate in higher education \cite{o2014front}. Therefore, both perspectives
are complementary and play different roles in promoting the learning process;
however, there is a certain degree of incompatibility that would hinder the
process of adoption of a single messaging service that fits the need of both
collectives, or would favor the adoption of semi-informal solutions that would
rely on a popular platform (such as WhatsApp or Telegram) enhanced with
institutional agreements with their providers, as well as locally created and
supported chatbots.
